Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-05-02 tex/scam/reviews-v1/response-v1.tex

We sometimes need a notation for the distribution because we want to write $L^2(P), L_2(P)$ to represent, respectively, the Hilbert space of square integrable functions and the $L_2$-norm with respect to the distribution $P$. We have removed any mention of the distribution where it is not necessary.

We have changed all ``F'' to ``P'' to represent the distribution, and, to avoid confusing the density with the dimensionality, we now write $p(x)$ instead of just $p$ whenever we refer to the density. We believe that this change, along with the context, are enough to disambiguate the two quantities.

\item \rc{I would suggest including the dependence on the positive-valued lower
bound on $p(x)$ (as assumed in (A5)) in the statement of Theorem 3. This
is a point worth commenting upon, since the earlier theorems only
require $p(x)$ to be strictly positive. Assumption (A5) seems like it
could also be interpreted as a sort of minimum signal strength
requirement for successful variable selection.}

We have added the dependence on the lower bound $c_l$ of $p(x)$ in Theorem 5.2, where we require that $p \leq O(\exp(cn))$ for $c < \frac{c_l}{32}$. We have also added the dependence on the upper bound $c_u$ of the density in Theorem 5.3. The lower and upper bounds $c_l, c_u$ do not directly play the role of the signal level; they are used to simplify technicalities in the presentation and the proof of the theorems. For example, Theorem 5.2 should also go through if one assumes only that the marginal densities $p(x_j)$'s are positive on a sub-interval of $[-1,1]$.

@@

The conditions in Theorem 5.1 are indeed analogous and we have edited the remark accordingly. The conditions in Theorem 5.1 are much more strict than the mutual incoherence condition though.

\item \rc{In the simulation section, the authors might consider comparing the
set of variables selected after the AC step only with the set of
variables selected via the entire AC/DC algorithm. This would help
illustrate the necessity of the concave fitting step in addition to
the convex additive fit alone.}

We have added an additional simulation comparing the variables selected via the AC stage and the DC stage. Please see the last paragraph in Section 6.1 as well as Figure 6. The DC stage is slightly helpful in recovering the true variables but its effect is insignificant. We believe that the DC stage is important in theory but not so in practice.

Minor typos:
\begin{enumerate}[(i)]
\item \rc{In Section 2.3, it would be good to actually state the regularized
objective function being analyzed, rather than waiting until Section
4.}

We have added the objective function in Section 2.2 where we summarize the optimization algorithm.

\item \rc{Assumption (A3) on page 7 is missing the subscript $\infty$.}

The missing subscript is added.

\item \rc{The parameter $\sigma$ is never defined in Section 2.3. Reading ahead,
it seems to be the sub-Gaussian parameter of the additive noise.}

$\sigma$ has been defined in Section 2.3.

\item \rc{Perhaps Section 3 should be titled something other than ``Additive
faithfulness'' (maybe ``Population- level results''?).}

\item \rc{The first paragraph of Section 5 should read
  ``Figure 3'' rather than ``Algorithm 3.''}

Corrected.

\item \rc{The second paragraph of Section 5 has $m\hat{}u$ instead of $\hat\mu$.}

Corrected.

\item \rc{The first sentence of Section 5.1 should read optimization (4.8).}

Corrected.

### 2015-05-02 tex/scam/sparsistency.tex
more responses

Our goal is to show that variable screening consistency. That is, as $n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 0 where $\hat{S}$ is the set of variables outputted by AC/DC in the finite sample setting (Algorithm~\ref{fig:backfitting:algo}) and $S$ is the set of variables outputted in the population setting~\eqref{eqn:acdc_vars_pop}.

>>>>

Our goal is to show that variable screening consistency. That is, as $n,p \rightarrow \infty$, $\mathbb{P}( \hat{S} = S)$ approaches 0 where $\hat{S}$ is the set of variables outputted by AC/DC in the finite sample setting (Figure~\ref{fig:backfitting:algo}) and $S$ is the set of variables outputted in the population setting~\eqref{eqn:acdc_vars_pop}.
